Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-10-06 manuscript/climate_sensitivity_draft.Rmd
social media/ orcid updates
more social media/ orcid

Joseph Zailaa: 
https://twitter.com/ZailaaJ

Neil Pederson:
https://twitter.com/YellowBuckeye,
https://www.facebook.com/neil.pederson.5,
https://www.instagram.com/1yellowbuckeye/

Kristina Anderson-Teixiera:
https://twitter.com/K_A_Teixeira

Ian R. McGregor:
https://twitter.com/realclimatian

@@

**These need complete names, ordering**

Ian R. McGregor: https://orcid.org/0000-0002-5763-021X

Norbert Kunert: https://orcid.org/0000-0002-5602-6221

Alan Tepley: https://orcid.org/0000-0002-5701-9613

Neil Pederson: https://orcid.org/0000-0003-3830-263X

Bourg: 0000-0002-7443-1992

McShea: 0000-0002-8102-0200

Joseph: https://orcid.org/0000-0001-9103-190X

Kristina J. Anderson-Teixeira: https://orcid.org/0000-0001-8461-9713

>>>>

**Brief Heading:** Tree-rings reveal how tree height and leaf traits shape drought tolerance in a broadleaf forest

Ian R. McGregor:

https://twitter.com/realclimatian

Joseph Zailaa:

https://twitter.com/ZailaaJ

Atticus E.L. Stovall:

https://twitter.com/StovallAtticus

Neil Pederson:

https://twitter.com/YellowBuckeye,

https://www.facebook.com/neil.pederson.5,

https://www.instagram.com/1yellowbuckeye/

Kristina Anderson-Teixiera:

https://twitter.com/K_A_Teixeira

@@

Ian R. McGregor: 0000-0002-5763-021X

Norbert Kunert: 0000-0002-5602-6221

Alan J. Tepley: 0000-0002-5701-9613

Erika B. Gonzalez-Akre: 0000-0001-8305-6672

Valentine Herrmann: 0000-0002-4519-481X

Joseph Zailaa: 0000-0001-9103-190X

Atticus E.L. Stovall: 0000-0001-9512-3318

Norman A. Bourg: 0000-0002-7443-1992

William J. McShea: 0000-0002-8102-0200

Neil Pederson: 0000-0003-3830-263X

Lawren Sack: 0000-0002-7009-7202

Kristina J. Anderson-Teixeira: 0000-0001-8461-9713
